Think deep for reef resilience

### 2025-08-10 paper/paper_draft.qmd
Add limitation section

@@

>>>>

## Limitations

@@

Additionally, it is currently not possible to obtain highly accurate and precise estimates
of reef depth at the GBR-scale. Data adopted for the given assessment are said to be
accurate up to 15m from Mean Sea Level [@GBRMPA2020], however there are many sources of
uncertainty in the depth estimates used for this study. Satellite-derived estimates are
subject to different bottom types (rock, sand, seagrass, etc) and how these affect
reflectance, the water penetration depth of satellite sensors, influence of local conditions
(e.g., turbidity and wave activity), among many other factors.

In addition to the usual challenges of deriving data from satellite imagery, it is
acknowledged that there is high potential for misalignment between the bathymetry data and
GBRMPA reef outlines. Hammerton and Lawrey [-@hammerton], for example, identified 120 false
positives, where features identified as reefs were in actuality sand banks or rocky reefs
(rather than coral reefs). Reefs with bathymetry data of less than 5% of its indicative area
were excluded from analysis to ensure analyses were not conducted on reefs with no data
coverage (see @sfig-depth-cutoff). The existing GBRMPA reef outlines were adopted to align
with other ongoing modelling and analyses conducted as part of the Reef Restoration and
Adaptation Program (RRAP; <https://gbrrestoration.org>) **\[TODO: PROPER CITATION OF
RRAP\]**. The median depths for each indicative reef area were extracted from bathymetry
data using zonal statistics and depth values beyond the 15m range were included. The
resulting depth estimates are therefore highly uncertain and are only adopted as a useful
indication for the purpose of the presented analysis. They are not intended to be an
accurate and precise report of reef depths across the GBR.

**\[TODO - rewrite/expand paragraphs below for flow\]**
